\chapter{Ethics Submission}

% This appendix includes a copy of the ethics submission for the project. After you have completed your Ethics submission, you will receive a PDF with a summary of the comments. That document should be embedded in this report, either as images, an embedded PDF or as copied text. The content should also include the Ethics Application Number that you receive. 

Assessment ID (reference): 15664

12/03/2020
For your information, please find below a copy of your
recently completed online ethics assessment

Next steps

Please refer to the email accompanying this attachment for details on the correct ethical
approval route for this project. You should also review the content below for any ethical
issues which have been flagged for your attention

Staff research - if you have completed this assessment for a grant application, you are not
required to obtain approval until you have received confirmation that the grant has been
awarded.

Please remember that collection must not commence until approval has been confirmed.

In case of any further queries, please visit www.aber.ac.uk/ethics or contact
ethics@aber.ac.uk quoting reference number 15664.

Assesment Details

AU Status
Undergraduate or PG Taught

Your aber.ac.uk email address
srj12@aber.ac.uk

Full Name
Samuel Robert Jones

Please enter the name of the person responsible for reviewing your assessment.
Reyer Zwiggelaar

Please enter the aber.ac.uk email address of the person responsible for reviewing
your assessment
rrz@aber.ac.uk

Supervisor or Institute Director of Research Department
cs

Module code (Only enter if you have been asked to do so)
CS39440

Proposed Study Title
Complete the Feline Adoption Agency App

Proposed Start Date
27 January 2020

Proposed Completion Date
01 June 2020

Are you conducting a quantitative or qualitative research project?
Mixed Methods

Does your research require external ethical approval under the Health Research
Authority?
No

Does your research involve animals?
Yes

Does your research involve human participants?
No

Are you completing this form for your own research?
Yes

Does your research involve human participants?
No

Institute
IMPACS

Please provide a brief summary of your project (150 word max)
CS31620 developed a prototype FAA app. This was left incomplete needing support for
many of the tabs. My task is to complete anything that was missing, and to improve any
areas as appropriate.

Where appropriate, do you have consent for the publication, reproduction or use of
any unpublished material?
Yes

Will appropriate measures be put in place for the secure and confidential storage of
data?
Yes

Does the research pose more than minimal and predictable risk to the researcher?
No

Will you be travelling, as a foreign national, in to any areas that the UK Foreign and
Commonwealth Office advise against travel to?
No

Please include any further relevant information for this section here:
If you are to be working alone with vulnerable people or children, you may need a
DBS (CRB) check. Tick to confirm that you will ensure you comply with this 
requirement should you identify that you require one.
Yes

Declaration: Please tick to confirm that you have completed this form to the best of
your knowledge and that you will inform your department should the proposal
significantly change.
Yes

Please include any further relevant information for this section here: