\chapter{Third-Party Code and Libraries}

% If you have made use of any third party code or software libraries, i.e. any code that you have not designed and written yourself, then you must include this appendix. 

% As has been said in lectures, it is acceptable and likely that you will make use of third-party code and software libraries. If third party code or libraries are used, your work will build on that to produce notable new work. The key requirement is that we understand what your original work is and what work is based on that of other people. 

% Therefore, you need to clearly state what you have used and where the original material can be found. Also, if you have made any changes to the original versions, you must explain what you have changed. 

% The following is an example of what you might say. 

% Apache POI library - The project has been used to read and write Microsoft Excel files (XLS) as part of the interaction with the client's existing system for processing data. Version 3.10-FINAL was used. The library is open source and it is available from the Apache Software Foundation 
% \cite{apache_poi}. The library is released using the Apache License 
% \cite{apache_license}. This library was used without modification. 

%Android SDK
Android SDK - The project used the SDK to compile the program for the Android Operating system, it was fundamentally crucial to the application's development and functionality to be included. Version 29.0.2 was used. The library and all documentation is provided under the Apache 2.0 License and was not modified.
\cite{APACHE2LICENSE}.

%Android X
Android X - Is a large library consisting on multiple smaller parts that are developed with the aim of improving backwards compatibility for modern Android application functionality. Android X was used for backwards compatible Navigation, layouts, testing, view model editing, and kotlin specific implementations. The following list describes all of the sub libraries used specifically which are also distributed open source under the Apache2.0 License and no libraries were modified. \cite{APACHE2LICENSE}
    \begin{itemize}
        \item androidx.appcompat:appcompat:1.1.0
        \item androidx.core:core-ktx:1.2.0
        \item androidx.constraintlayout:constraintlayout:1.1.3
        \item androidx.gridlayout:gridlayout:1.0.0
        \item androidx.navigation:navigation-ui-ktx:2.3.0-alpha04
        \item androidx.navigation:navigation-fragment-ktx:2.3.0-alpha04
        \item androidx.legacy:legacy-support-v4:1.0.0
        \item androidx.lifecycle:lifecycle-extensions:2.2.0
        \item androidx.lifecycle:lifecycle-viewmodel-ktx:2.2.0
        \item androidx.test.ext:junit:1.1.1
        \item androidx.test.espresso:espresso-core:3.2.0
        \item androidx.navigation:navigation-testing:2.3.0-alpha04
        \item androidx.test:rules:1.3.0-alpha05
    \end{itemize}


% Firebase
Firebase - is a set of libraries and source codes that are developed to work in tandem with the Google Firebase services for application development, they are fundamental to the core of the applications, Authentication, Notifications, Database, Image hosting, and some UI elements. These are provided as open source under a Apache 2.0 License and no library modifications were made. \cite{APACHE2LICENSE} The following list are specific libraries used.
    \begin{itemize}
        \item com.google.firebase:firebase-analytics:17.3.0
        \item com.google.firebase:firebase-auth:19.3.0
        \item com.firebaseui:firebase-ui-auth:6.2.0
        \item com.google.firebase:firebase-firestore-ktx:21.4.2
        \item com.firebaseui:firebase-ui-firestore:6.2.0
        \item com.google.firebase:firebase-database-ktx:19.2.1
        \item com.firebaseui:firebase-ui-database:6.2.0
        \item com.google.firebase:firebase-messaging:20.1.4
        \item com.google.gms.google-services
    \end{itemize}
    
% Picasso
Picasso - A library that is aimed at loading images from a url either online or offline and from the file store asynchronously into an Android Image View. These are provided under an Apache 2.0 License and no library modifications were made. \cite{APACHE2LICENSE} The version of the library used is 2.71828. 

% Material
Material Design - The library built to assist in the production of material design guided software, specifically used for the Material Design theme, \gls{Bottom Navigation Bar} and Material \gls{Card}. Open source and Provided under a Apache 2.0 license and was not modified \cite{APACHE2LICENSE}. Version used is 1.2.0-alpha05.

% Gradle
Gradle - The build system of choice when running Android Studio for development, it is crucial for building, testing and developing for the Android SDK. Open source and provided under an Apache 2.0 License and no library modifications were made \cite{APACHE2LICENSE}.

% Kotlin
Kotlin - Is the programming language of choice created by JetBrains as an alternative to a pure Java implementation, almost all of the project relies on Kotlin. Open source and provided under an Apache 2.0 license and no library modifications were made \cite{APACHE2LICENSE}. The Kotlin version in use is 1.3.71.