\chapter{Technical Requirements} \label{TECHREQUIREMENTS}

\begin{itemize}
    \item All Activities, and the app as a whole should be made using Material Design Guidelines
    \item Using the latest Android Navigation library will allow me to integrate correct navigation easily between Activities
    \item The home activity should display some stuff
        \begin{itemize}
            \item Cat of the month
            \item First 3 saved cats if signed in, if not signed in recommend 3 cats to adopt.
            \item If signed in also progress on your adoptions in a RecycleView at the top of the page.
        \end{itemize}
    \item An activity that allows a person to find a cat to adopt similar to Cats Protection's find-a-cat. This should be a list, probably a RecyclerView that has a MaterialCard that allows us to view some basic details and save, basic details include:
        \begin{itemize}
            \item Age
            \item Sex
            \item Name
            \item Location
            \item Cat Picture
        \end{itemize}
    \item Each cat found on the cat finder tool should have it's own popup Activity that displays multiple details:
        \begin{itemize}
            \item Cat Picture
            \item Age
            \item Sex
            \item Name
            \item Small paragraph with some details about the cat's history (Will contain disability info if present)
            \item Breed
            \item Location
            \item Colour
            \item Disabled
            \item Cat Preferences:
            \begin{itemize}
                \item Likes kids - Different ages of kids (Secondary, primary, younger)
                \item Families
                \item Indoors
                \item Other cats
                \item Dogs
            \end{itemize}
            \item Allow a cat to be saved
            \item Allow show of interest ("Adopt" button) needs an info icon that when tapped explains what that button does. Requires a user to login before process works. Pop up asking a user to login, if not already logged in.
        \end{itemize}
    \item An activity where you can display any "Saved" cats
    \item When the adopt button is clicked on a cat (and logged in, if not ask to login), propose a home visit time for an admin to complete.
    \item The home, saved, and cat finder tool should appear on the bottom navigation bar.
    \item There should be a Navigation Draw which contains links to multiple activities, including the home, saved, and cat finder tool. Also it should contain a link to standalone activities:
        \begin{itemize}
            \item About us
            \item Help and Feedback
            \item Log in (Using OAuth) for users
                \begin{itemize}
                    \item This will be replaced with a My Account activity after login
                \end{itemize}
            \item Permissions for any licensed content, possibly in the About us screen
            \item Settings
        \end{itemize}
    \item Toolbar, containing buttons to access the NavigationDraw, settings and up button.
    \item User accounts should provide people with the ability to:
        \begin{itemize}
            \item Sync Data across devices, i.e. their saved cats
            \item Request to adopt a cat
            \item View their status for approval of adoption of a cat
        \end{itemize}
    \item The app should rely on a stable database provided by a university hosted container or other secure source, the code/schema for this database should be seperate from the code for the app, but both should be in the Git Repository alongside documentation
    \item The database should be filled with data that has been made up.
    \item Any used cat images should be provided with a free to use license clearly visible if required.
    \item The app should use the icon that has been made for the occasion
    \item Integration UI testing for each concievable workflow on each Activity in the application
    \item All testing should be done on a separate "testing" database, no testing should be done on the "live" database, unless manually performed
    \item All non-UI activity specific code should have unit tests associated with it.
\end{itemize}

